%%% Please fill in basic information on your thesis, which will be automatically
%%% inserted at the right places.

% Type of your thesis:
%	"bc" for Bachelor's
%	"mgr" for Master's
%	"phd" for PhD
%	"rig" for rigorosum
\def\ThesisType{bc}

% Language of your study programme:
%	"cs" for Czech
%	"en" for English
\def\StudyLanguage{cs}

% Thesis title in English (exactly as in the official assignment)
% (Note: \xxx is a "ToDo label" which makes the unfilled visible. Remove it.)
\def\ThesisTitle{\xxx{Artificial Intelligence for the Board Game Sagrada}}

% Author of the thesis (you)
\def\ThesisAuthor{\xxx{Ákos Vermes}}

% Year when the thesis is submitted
\def\YearSubmitted{\xxx{2024}}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% see https://www.mff.cuni.cz/en/faculty/organizational-structure,
% or a full name of a department outside MFF)
\def\Department{\xxx{Department of Software and Computer Science Education (KSVI)}}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{\xxx{Department}}

% Thesis supervisor: name, surname and titles
\def\Supervisor{\xxx{Adam Dingle, M.Sc}}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{\xxx{Department of Software and Computer Science Education (KSVI)}}

% Study programme (does not apply to rigorosum theses)
\def\StudyProgramme{\xxx{Computer Science (B0613A140006)}}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, who provided you with tea and pizza, etc.)
\def\Dedication{%
\xxx{I want to express my heartfelt appreciation to Adam Dingle for his incredible support and patience throughout this journey.
His guidance was extremely helpful, especially during the times when the process took longer than expected. 
The tools he introduced for software and AI development were crucial to the success of this project and I have learned a lot from him.
}
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%
\xxx{The application of artificial intelligence to board games has become widespread in recent years inspired by achievements in chess and Go.
This thesis presents a detailed exploration of artificial intelligence techniques in an implementation of the board game Sagrada.
Sagrada presents challenges for artificial intelligence agents due to the complexity of the game, the high branching factor and the presence of hidden and stochastic 
information in the game. The primary focus of the thesis is on implementing and comparing the performance of minimax, Monte Carlo Tree Search (MCTS), 
and rules-based algorithms.
  }
}

% 3 to 5 keywords (recommended) separated by \sep
% Keywords are useful for indexing and searching for the theses by topic.
\def\ThesisKeywords{%
\xxx{artificial intelligence\sep board game\sep heuristic}
}

% If any of your metadata strings contains TeX macros, you need to provide
% a plain-text version for use in XMP metadata embedded in the output PDF file.
% If you are not sure, check the generated thesis.xmpdata file.
\def\ThesisAuthorXMP{\ThesisAuthor}
\def\ThesisTitleXMP{\ThesisTitle}
\def\ThesisKeywordsXMP{\ThesisKeywords}
\def\AbstractXMP{\Abstract}

% If your abstracts are long and do not fit in the infopage, you can make the
% fonts a bit smaller by this setting. (Also, you should try to compress your abstract more.)
\def\InfoPageFont{}
%\def\InfoPageFont{\small}  % uncomment to decrease font size

% If you are studing in a Czech programme, you also need to provide metadata in Czech:
% (in English programmes, this is not used anywhere)

\def\ThesisTitleCS{\xxx{Umělá inteligence pro deskovou hru Sagrada}}
\def\DepartmentCS{\xxx{Katedra softwaru a výuky informatiky (KSVI)}}
\def\DeptTypeCS{\xxx{Katedra}}
\def\SupervisorsDepartmentCS{\xxx{Katedra softwaru a výuky informatiky (KSVI)}}
\def\StudyProgrammeCS{\xxx{Informatika (B0613A140006)}}

\def\ThesisKeywordsCS{%
\xxx{umělá inteligence\sep desková hra\sep heuristika}
}

\def\AbstractCS{%
\xxx{Aplikace umělé inteligence na deskové hry se v posledních letech rozšířila, což bylo inspirováno úspěchy ve šachu a Go.
Tato práce představuje podrobný průzkum technik umělé inteligence v implementaci deskové hry Sagrada.
Sagrada představuje pro hráče řízené umělou inteligencí výzvy kvůli složitosti hry, vysokému větvení a přítomnosti skrytých a stochastických informací ve hře.
Hlavním zaměřením práce je implementace a srovnání výkonu algoritmů minimax, Monte Carlo Tree Search (MCTS) a algoritmů založených na pravidlech.}
}
